% Content for Trophies

\paragraph{}
Overall General Championship Trophy will be a rolling trophy. Any IIT that wins the Trophy for 3 consecutive years shall take permanent ownership the trophy and a new trophy shall be made for further meets.

\paragraph{}
The Overall General Championship Trophy of the InterIIT Tech Meet will be a rolling trophy, awarded annually to the IIT securing the highest overall score across all events.

\paragraph{}
In the event that an IIT wins the Overall General Championship for three consecutive years, that IIT shall be conferred permanent ownership of the trophy. A new trophy shall thereafter be made for subsequent editions of the Tech Meet.

\paragraph{}
The IIT declared as the overall winner will be responsible for the safekeeping of the trophy and must physically return the trophy to the Organising Committee of the next Host IIT within a stipulated time prior to the commencement of the opening ceremony of the following Tech Meet. In case of damage, it should be reported to the Host IIT and the trophy should still be returned to the Host IIT. 

\paragraph{}
Failure to comply will result in withholding of overall scores for that IIT for a period of 1 year.



\begin{enumerate}
    \item In the case of a tie in the overall points between multiple IITs, the IIT with the greater number of Gold medals will be declared winners,
    \item In the case that number of Gold medals match for multiple IITs, the IIT with the greater number of Silver medals will be declared winners,
    \item In the case that the number of Silver medals match for multiple IITs, the IIT with the greater number of Bronze medals will be declared winners,
    \item In the case the overall points and number of Gold, Silver and Bronze medals match for multiple IITs, the IITs will be declared as joint winners,
    \item In case of joint winners, the Rolling trophy shall be kept at each IIT for an equal amount during the year, the order for keeping the trophy can be decided by mutual consensus or by random allotment process,
    \item Certificate of honor and a memento shall be awarded to all members winning the Gold/Silver/Bronze medals in a particular event,
    \item Certificate of participation shall be awarded to all registered members of the contingent, subject to the limits of each problem statement,
\end{enumerate}
