\subsection{Vision}
\paragraph{}
India is a developing country. There are countless problems that it faces due to its population,  geographic expanse, climate, infrastructure, and various other factors. A lot of efforts are being put in by various educational institutes for coming up with technology solutions that could address these issues. Numerous government policies and initiatives have created opportunities for promoting and encouraging the development of technology to address these issues. The IITs being premier education and research institutes, spearhead these initiatives. Enhanced collaboration between IITs would foster the development of technology solutions and also encourage more and more graduating students to pursue this into full-time ventures wherein they take this technology from research labs to end users, impacting a million lives. Inter IIT Tech Meets are envisioned to challenge participants to come up with technological solutions for the problems, compete with teams in a healthy environment, interact with like-minded people across the country, and promote the transfer of this technology to ventures which will address problems at grass-root levels.

\subsection{Mission}
\paragraph{}
The InterIIT Tech Meets will strive towards the vision by
\begin{enumerate}
    \item Coming up with problem statements for the event which
    \begin{enumerate}
        \item Address commonly faced problems by millions around the world, issues which are relevant to a social cause,
        \item Address industrial problems and come up with a working prototype and aim towards taking this to implementation of technology in the industry,
        \item Improve the living standards or ease life by suitable intervention of technology and/or its improved management,
        \item Enhance collaboration and boost technology development.
    \end{enumerate}
    \item To serve as a platform for
    \begin{enumerate}
        \item Fair and healthy competition between teams and support the teams to come up with their best as they compete,
        \item Social entrepreneurs, businesses, and NGOs who are willing to take forward these technology solutions from research labs to the millions who will be impacted by this,
        \item Address industry-academia gaps through networking activities and challenges where diverse teams attempt to solve the problem,
        \item Interaction of people belonging to different segments of the technical community to initiate community development through collaboration and serve a larger socio-economic purpose.
    \end{enumerate}
\end{enumerate}

\paragraph{}
The Tech Meet will have various events which will have some elements of competitiveness which ensure the best efforts are put in while coming up with solutions and building the technology that goes beyond the competition and improvise the solution based on feedback and enter the market as a competitive solution or be a stepping stone to fundamental or applied research and development.