% Content for Eligibility
\paragraph{}
All bonafide full time students of all IITs, who will be getting degree/diploma from the concerned IIT, are eligible to participate. A consolidated list of the contingent members, attested as bonafide students by the Dean of Students/Registrar of concerned IIT, should be submitted to the Chairman of the Tech Meet before a stipulated time before commencement of meet.

\subsection{Eligibility of Participating IIT}
\paragraph{}
Pandit Jawaharlal Nehru pioneered the establishment of the Indian Institutes of Technology to provide trained technical personnel of international class to the nation who would act as leaders in technology for the newly born independent India. For an IIT to be a part of the InterIIT Tech Meet, it 
\begin{enumerate}
    \item Should be recognised as an Indian Institute of Technology by the IIT Council established by the IIT Act,
    \item Have an active student body to oversee participation
\end{enumerate}

\subsection{Eligibility of Participating Students}

\paragraph{}
For a student to participate in the InterIIT Tech Meet, they should meet all of the following criteria
\begin{enumerate}
    \item Currently enrolled in an IIT which is eligible to participate in the InterIIT Tech Meet,
    \item Currently enrolled in a full time offline academic program whose entire duration should be greater than 18 months,
    \item Currently not a part of an exchange program to visit the IIT which they wish to represent.
\end{enumerate}

\paragraph{}
If a student is enrolled in a Joint-Degree program then the following eligibility criteria applies
\begin{enumerate}
    \item At least one of the participating Institutes in the joint degree should be an IIT eligible to participate in the InterIIT Tech Meet, said student can only represent an IIT which is eligible,
    \item Currently enrolled in a full time offline academic program whose entire duration should be greater than 18 months,
    \item Complete at least one semester at the IIT on behalf of which they wish to participate before the commencement of the offline event,
    \item Currently not a part of an exchange program to visit the IIT on behalf of which they wish to participate.
\end{enumerate}

\paragraph{}
If the candidate is eligible to participate on behalf of more than one IIT, they can choose the IIT they wish to represent. A student can represent only one IIT in a given edition of InterIIT Tech Meet. 

\paragraph{}
It shall be the sole responsibility of the representatives of each participating IIT to ensure that only eligible students are registered for participation. The Organising Committee reserves the right to verify the eligibility of registered students. Any deviation from the prescribed norms or non-compliance with the eligibility criteria shall result in the disqualification of the concerned contingent from the specific problem statement(s) involved.