% Content for General Rules
\begin{enumerate}
    \item The Tech Meet will be hosted by the Host IIT at its campus for a minimum of 2 days to a maximum of 5 days. It will be an annual event.
    \item The Host IIT shall be responsible for drafting the Rule Book, which shall comprise of
    \begin{enumerate}
        \item the rules and regulations which all the participating IITs must abide by,
        \item the maximum size of the contingent for individual events in High Prep, Mid Prep and Low/No Prep categories,
        \item the list of tentative domains and event details planned for the year,
        \item a detailed scoring system for each of High Prep, Mid Prep and Low/No Prep events,
        \item any additional rules for penalties applied to various violations,
    \end{enumerate}
    and shall be accepted pending ratification at the Board meeting.
    \item The name of IITs shall strictly not be disclosed at any point of time during the competition to the judges.
    \item The Host IIT is expected to setup an official communication forum which shall be utilized by all IITs to propose suggestions, discuss concerns or objections regarding any and all issues pertaining to the Tech Meet.
    \item The Host IIT is expected to release the tentative list of domains at the earliest, which is to be notified through the communication channel.
    \item It is mandatory for the Host IIT to finalize all the domains for the problem statements by the pre-decided dates set during the Board Meeting. The problem statements shall be frozen by at least 7 days before the commencement of first High Prep, Mid Prep and at least 15 days prior for Low/No Prep Events.
\end{enumerate}

\subsection{Code of Conduct}
\begin{enumerate}
    \item Intentional damage to competition setups/ practice setups, the infrastructure of Host IIT at competition venue or to demonstration/setup of other IITs can result in disqualification in the event,
    \item Usage of pirated/unauthorized versions proprietary software technologies during any stage of competition or development of prototype/demonstration if found will lead to disqualification of entry in that particular event.
    \item Violation of standard safety rules mentioned in the Rulebook while operating equipment or giving demonstrations may lead to penalties ranging from event score reduction to disqualification. The penalty is left to the discretion of judges during the event,
    \item Any individual if found involved in any prohibited activities/areas of the Host IIT shall be banned from participation in the Tech Meet of the particular year. The Host IITs are advised to include a list of such prohibited areas/activities inside their campus.
\end{enumerate}

\begin{enumerate}
    \item The Tech Meet will be hosted by the Host IIT at its campus for a minimum of 2 days to a maximum of 5 days. It will be an annual event.
    \item The Organising Team shall be responsible for drafting the Rule Book which outlines important information for that edition of InterIIT Tech Meet and shall be accepted pending ratification at the Board meeting.
    \item The name of IITs shall strictly not be disclosed at any point of time during the competition to the judges. 
    \item The Organising Team is expected to set up an official communication forum which shall be utilized by all IITs to propose suggestions, discuss concerns or objections regarding any and all issues pertaining to the Tech Meet.
    \item The Organising Team is expected to release the tentative list of domains at the earliest, which is to be notified through the communication channel.
    \item It is mandatory for the Organising Team to finalize all the domains for the problem statements by the pre-decided dates set during the Board Meeting. The problem statements shall be frozen by at least 7 days before the commencement of first High Prep, Mid Prep and at least 15 days prior for Low/No Prep Events.
\end{enumerate}

\subsection{Code of Conduct}
\begin{enumerate}
    \item Intentional damage to competition setups/ practice setups, the infrastructure of Host IIT at competition venue or to demonstration/setup of other IITs can result in disqualification in the event,
    \item Usage of pirated/unauthorized versions proprietary software technologies during any stage of competition or development of prototype/demonstration if found will lead to disqualification of entry in that particular event.
    \item Violation of standard safety rules mentioned in the Rulebook while operating equipment or giving demonstrations may lead to penalties ranging from event score reduction to disqualification. The penalty is left to the discretion of judges during the event,
    \item Any individual if found involved in any prohibited activities/areas of the Host IIT shall be banned from participation in the Tech Meet of the particular year. 
\end{enumerate}

\subsection{Rulebook}
The rulebook should mandatorily contain the following:
\begin{enumerate}
    \item The rules and regulations which all the participating IITs must abide by,
    \item List of prohibited areas and activities in the Host IIT,
    \item Dates of the offline InterIIT Tech Meet with date and time of commencement and termination of accommodation and food services,
    \item The maximum size of the contingent for individual events, such as, in High Prep, Mid Prep and Low/No Prep categories,
    \item The list of tentative domains and event details planned for the year,
    \item Dates and/or date ranges for release of different problem statements and/or events
    \item A detailed scoring system for each of High Prep, Mid Prep and Low/No Prep events,
    \item Last date of submission deadline of the problem statements. This date should be no later that 3 days prior to the date of commencement of the Tech Meet,
    \item Official Communication forum(s) that will be used during the Tech Meet. In case multiple forums are used, a clear set of precedence should be mentioned,
    \item Detailed guidelines of procedure of registration of participating IITs, their admin members and participants of individual events,
    \item Registration, food, accommodation and any other fees that is to be paid by the participating IITs and/or its admin/participants along with appropriate deadlines and procedure of payment and verification,
    \item Discuss the format of submission of problem statements as well as a contingency submission route in case of emergencies,
    \item Any additional rules for penalties applied to various violations, 
    \item Final date or date-range of release of any submission guidelines for individual events before the deadline of the full submission,
    \item Deadline of submission of any and all mid-term and end-term submissions of problem statements,
    \item Discuss policy on usage of paid API/software in generating solutions,
    \item Discuss policy on any on-spot type evaluation,
    \item Discuss policy on IP rights for individual events,
    \item Guidelines and procedure of handling contentions,
    \item Details of Convener(s).
\end{enumerate}


