% Content for Host Selection
\paragraph{}
The Host for the next InterIIT Tech Meet shall be decided at the ad-hoc Tech Board Meeting conducted before the end of the academic year. Each IIT willing to host the next InterIIT shall submit a proposal approved by the Director of their institute and shall submit the same to the Chairman of the Tech Board. In the event there is only a single IIT submitting a proposal, it shall be declared as Host IIT for the next InterIIT Meet. In an event where there are more than one IITs submitting proposals, there shall be a discussion of the proposals by the Tech Board. The Host will then be decided by preferential voting. The host IIT cannot submit a proposal for hosting the next edition during the second Tech Board Meeting. In the event that no IIT submits a proposal, the Chairman of the Tech Board shall invite proposals from Directors of IITs. At this stage, the Host IIT is also eligible to apply.

\begin{enumerate}
    \item The Host for the next InterIIT Tech Meet shall be decided at the ad-hoc Tech Board Meeting conducted before the end of the academic year.
    \item Each IIT willing to host the next InterIIT shall submit a proposal approved by the Director of their institute. Such a proposal shall be submitted, via email, by a member-email of the Board to the Chairman of the Tech Board and copy it to all members of the Board. A list of emails of members of the Tech Board shall be maintained in appendix C. 
    \item In the event there is only a single IIT submitting a proposal, a majority vote by the IITs present in the Tech Board meeting is required for declaring the applying IIT as the Host IIT for the next InterIIT Meet. In case, the applying IIT fails to get such a vote, it shall modify its proposal to meet the suggestions made by the Board. The new proposal should be resubmitted and discussed in a Tech board meeting.
    \item In an event where there are more than one IITs submitting proposals, there shall be a discussion of the proposals by the Tech Board. The Host will then be decided by preferential voting. The Host IIT cannot submit a proposal for hosting the next edition during the second Tech Board Meeting. 
    \item In the event that no IIT submits a proposal, the Chairman of the Tech Board shall invite proposals from Directors of IITs. At this stage, the Host IIT is also eligible to apply.

\end{enumerate}

\subsection{Guidelines}
\paragraph{}
The proposal should be submitted with a cover letter attested by the Director of the Institute.
It should contain details on the following:
\begin{enumerate}
    \item Details of participation of the IIT in previous InterIIT Tech Meets,
    \item Details of hosting of the InterIIT Tech Meet or events of similar scale in the past,
    \item Details of organising team structure and tentative dates for hosting the meet,
    \item Details of accommodation capacity, infrastructure which will be needed for hosting the InterIIT Tech Meet,
    \item Details of new initiatives, long-term problem statements that they wish to bring in the Inter IIT Tech Meet should be discussed.
\end{enumerate}
