% Content for Host Responsibilities
\paragraph{}
The Host IIT is responsible for organising the InterIIT Tech Meet of the current year. They have the following responsibilities:
\begin{enumerate}
    \item Appoint organising team to manage the affairs of the event, its planning, execution and acceptable closure of the event. This organising team will be led by 1 or 2 Convener(s). The Convener(s) will serve as the point of contact for the participating IITs,
    \item Ideate and plan the events of the meet and manage the logistics for the event,
    \item Draft the Rulebook, that shall be used during the period of the competition,
    \item Maintain the official website and social media handles. An official web domain shall be established for all subsequent InterIITs. It is the responsibility of the Host IIT to bear the cost of the web domain during the period through which they bear the title of Host IIT. All access to the web domain shall be handed over to the next Host IIT upon the selection of the successor Host IIT,
    \item Make accommodation arrangements for Participating Contingents during the InterIIT Tech Meet,
    \item Make arrangements for judges, as applicable for the event,
    \item Ensure that the Contingent of Host IIT and the InterIIT Tech Meet Organizing team are completely independent and have no common members. In case of violation of this rule, the Host IIT will be disqualified for the events in which the common member was registered,
    \item Bear the cost of hosting the meet, which includes,
    \begin{enumerate}
        \item Infrastructure for the events - posters, setup for competitions, etc.,
        \item Merchandise for the participants,
        \item Judges - fees and transport,
        \item Medals and Certificates,
        \item Website and its maintenance.
    \end{enumerate}
\end{enumerate}

\paragraph{}
The Host IIT shall mention the basic amenities/facilities being by provided them in the Rulebook for the convenience of participants.

\paragraph{}
A nominal fee can be levied on each participant. This fee is to be decided by the Host IIT, and the breakdown of the same shall be included in the Rulebook.