% Content for Tech Board
\paragraph{}
The board shall be constituted for the purpose of effective supervision of the InterIIT Tech Meet. The headquarters of the Tech Board will be located at the host IIT. The Tech Board is constituted with the following members:
\begin{enumerate}
    \item Chairman of the InterIIT Tech Board (Director of Host IIT)
    \item Chairman of the InterIIT Tech Meet (Dean of Student Affairs of Host IIT or any equivalent institute functionary)
    \item Convener(s) of the InterIIT Tech Meet
    \item Representation from all IITs consisting of General Secretary Technical Affairs (or equivalent institute functionary), and the Contingent Leader.
\end{enumerate}

\paragraph{}
The Chairman of the Tech Board shall preside over all meetings. In their absence, the Convener of the Tech Meet shall occupy the chair and conduct the proceedings of the meetings. In the absence of the Chairman and the Convener, a nominee appointed by the Chairman/Convener will occupy the chair and conduct the proceedings of the meetings. The minutes of all the meetings shall be recorded and circulated to the members of all IITs after each board meeting.

\paragraph{}
The quorum for the conduction of the Tech Board meeting shall be representation from a minimum of half of all IITs. All decisions shall be passed on approval by a majority of votes of present IITs. Each IIT has one vote. In case of a tie, the Chairman or their nominee shall make the final decision.

\paragraph{}
The Tech Board Meeting will happen at least twice a year. The first board meeting should happen as soon as the academic year begins. This meeting will be held to decide the grounds for the problem statements for the year. This meeting to decide the initial structure of the InterIIT Tech Meet, events to be included, suggestions for the number of events, the genre of events and the timeline for finalization of the problem statements/events. The second board meeting should be conducted at the end of the InterIIT Meet for feedback and to decide the Host IIT for the next Inter IIT Tech Meet.

Host IIT should mandatorily conduct the following Tech Board Meetings:
\newpage
\begin{center}
\renewcommand\cellgape{\Gape[2pt]} % vertical padding inside makecell
\begin{longtable}{m{5cm} m{10cm}}
\hline
\\[-3pt]
\textbf{Timeline} & \textbf{Purpose}\\[4pt]
\hline
\\[-1pt]
At least 1 month before the release of the first problem statement for that year’s InterIIT Tech Meet &
\begin{enumerate}
    \item Decide the grounds for the problem statements for the year
    \item Decide the initial structure of the InterIIT Tech Meet, events to be included, suggestions for the number of events, the genre of events
    \item Timeline for finalization of the problem statements/events.
    \item Presentation and ratification of the rulebook
    \item Mandatory Open Session for presentation of Constitutional Amendments by participating IITs
\end{enumerate}
\\
\hline
Immediately after the conclusion of that year’s InterIIT Tech Meet &
\begin{enumerate}
    \item For levying penalties not mentioned in the Constitution
    \item Releasing of the provisional results for that year’s InterIIT Tech Meet
\end{enumerate}
\\
\hline
Within 2 months after the conclusion of that year’s InterIIT Tech Meet &
\begin{enumerate}
    \item For feedback to the Host IIT
    \item Presenting ideas for improving the construct of the InterIIT Tech Meet to the Tech Board
    \item For officially opening the floor for next year’s InterIIT Tech Meet
\end{enumerate}
\\
\hline
Within 2 weeks after the 3 week period from the submission of the first proposal for the following year’s hosting rights &
\begin{enumerate}
    \item To provide feedback on submitted proposals for hosting the following edition of the InterIIT Tech Meet
    \item To (reschedule another meet to) finalize the Host IIT for the following edition of the InterIIT Tech Meet
    \item Mandatory Open Session for presentation of Constitutional Amendments by participating IITs

\end{enumerate}
\hline
\end{longtable}
\end{center}




\paragraph{}
There is provision to host the Tech Board Meeting in the event that, the Tech Meet to be rescheduled/canceled due to unavoidable circumstances beyond the control of Host IIT.